---
title: "Data Visualization Project"
author: "Johnny Li"
output:
  pdf_document: default
  html_document: default
---

# Data Visualization Project

## Objectives for this project

To complete this project you’ll need to do a few things within this file. As you go through the notebook, you will have further instruction on how to complete these objectives.

1. Go through this notebook, reading along.

2. Fill in empty or incomplete code chunks when prompted to do so.

3. Run each code chunk as you come across it by clicking the tiny green triangles at the right of each chunk. You should see the code chunks print out various output when you do this.

4. At the very top of this file, put your own name in the `author:` place. Currently it says `"DataTrail Team"`. Be sure to put your name in quotes.

5. In the `Conclusions` section, write up responses to each of these questions posed here.

6. When you are satisfied with what you've written and added to this document you'll need to save it. In the menu, go to `File` > `Save`. Now the `nb.html` output resulting file will have your new output saved to it.

7. Open up the resulting `airbnb_project.nb.html` file and click `View in Web Browser`. Does it look good to you? Did all the changes appear here as you expected.

8. Upload your `Rmd` and your `nb.html` files to your assignment folder (this is something that will be dependent on what your instructors have told you -- or if you are taking this on your own, just collect these projects in one spot, preferably a Google Drive)!

7. Pat yourself on the back for finishing this project!

## The goal of this analysis

For this project, we are asking whether there are any relationships in Airbnb data? To answer this question, we will be taking data relating to Airbnb and using to data to create graphs to visualize the relationship between different variables in the data.

## Set up

Let's load these packages for use. Add or subtract from this list as you see fit.

```{r setup, include=FALSE}
## load packages
library(janitor)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(readr)
```


## Set up directories

Here we are going to make a `data` directory if it doesn't already exist.

```{r}
if (!dir.exists("data")) {
  dir.create("data")
}
```

## Get the data

The data we'll be using for this part of the project are about and can be downloaded from here: https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-01-24/readme.md

First, we'll read the data in from our `data/raw` directory. Use the `read_csv` function to do this. Call this new data frame `airbnb_df`.

```{r}
airbnb_df <- readr::read_csv("/cloud/project/04_Plotting_Data/data/raw/Airbnb_Open_Data.csv")
```

Use this chunk to do some exploring of this dataset to get an idea of what kind of information is here.

```{r, solution = TRUE}
dim(airbnb_df)
nrow(airbnb_df)
ncol(airbnb_df)
str(airbnb_df)
summary(airbnb_df)

max(airbnb_df$price, na.rm=T)
unique(airbnb_df$`room type`)
```

### Clean the data

Use the `janitor::clean_names` function to clean up some of these column names.

```{r, solution = TRUE}
colnames(airbnb_df)

airbnb_df <- airbnb_df %>% clean_names()
```

### Fix `neighbourhood_group` variable

Take a look at the `neighbourhood_group` variable. Try to summarize how many different neighborhood groups there are using the `summary()` function.

```{r, solution = TRUE}
### summary('neighborhood_group)
summary(unique(airbnb_df$neighbourhood_group))
```

You will find that this variable is a character, so we will need to check it as a factor to get meaningful information about the groups here. Thus run the `summary` function on a factor version of the `neighborhood_group` data, but don't yet change the variable to be a factor.

```{r, solution = TRUE}
airbnb_df$neighbourhood_group <- as.factor(airbnb_df$neighbourhood_group)
summary(airbnb_df$neighbourhood_group)
```

You'll notice there's some typos here `brookln` and `manhatan`. Fix these typos in this dataset by whatever method you find most intuitive. After you have fixed the typos, make sure that you coerce `neighbourhood_group` as a factor.

```{r, solution = TRUE}
airbnb_df$neighbourhood_group[airbnb_df$neighbourhood_group == 'brookln'] <- 'Brooklyn'
airbnb_df$neighbourhood_group[airbnb_df$neighbourhood_group == 'manhatan'] <- 'Manhattan'
```

Re-run `summary()` on the `neighbourhood_group` to see if your code successfully fixed these misspellings.

```{r, solution = TRUE}
summary(airbnb_df$neighbourhood_group)
```

### Fix numeric data

The `service_fee` and `price` columns are really numeric data but are being treated as characters because there are `$` and `,` included.

We'll need to get rid of these. **Hint** use this kind of code:
`stringr::str_remove(service_fee, "\\$|,")` within a mutate to get rid of the dollar signs. After you get rid of the dollar signs from both `service_fee` and `price`, coerce both of these variables to be numeric.

```{r, solution = TRUE}
airbnb_df <- airbnb_df %>% mutate(service_fee = as.numeric(stringr::str_remove(service_fee, "\\$|,")), price = as.numeric(stringr::str_remove(price, "\\$|,")))

class(airbnb_df$service_fee)
class(airbnb_df$price)
```

Use summary to see if `price` and `service_fee` are now appropriately numeric data.

```{r, solution = TRUE}
summary(airbnb_df$service_fee)
```

```{r, solution = TRUE}
summary(airbnb_df$price)
```

## Plot the data

Let's make a series of plots that explore how the price of an airbnb may be related to the other variables in this set.

To refresh your memory, a basic ggplot code looks like this:

```
DATA_FRAME %>%
  ggplot(aes(VARIABLE, VARIABLE, color = OPTIONAL_VARIABLE)) +
  geom_PLOT_TYPE()
```

We recommend keeping the ggplot2 cheatsheet handy while you are going through this project:
https://www.rstudio.com/resources/cheatsheets/

### Scatter plot

Now make a scatter plot that explores if `price` is related to one of the other numeric variables in the dataset.

```{r, solution = TRUE}
airbnb_df %>% ggplot(aes(x = price, y = service_fee)) + geom_point()
```

### Violin plot

Make a violin plot for the price distribution of different neighborhood groups.

```{r, solution = TRUE}
ggplot(data = airbnb_df, aes(x = price, y = room_type)) + geom_boxplot(fill = "pink", alpha = 0.9) + labs(title = "Relationship between Price and Room Types of AirBnbs") + scale_x_continuous(breaks = seq(0 , 1000, by = 100)) + xlab("Price") + ylab("Room Types") + theme_bw()
```

### Barplot

Now make a plot that explores if there's a particular `room_type` that has a higher price than others. You may choose to summarize the `price` by the `room_type`.  Hint: you may need to `group_by` a variable.    

```{r, solution = TRUE}
airbnb_df %>% group_by(room_type) %>% summarize(pricenew = mean(price, na.rm = T)) %>% ggplot(aes(x = room_type, y = pricenew)) + geom_bar(stat="identity", fill = "green")

```

### Your choice plot!

Make one more plot that is completely your choice about what variables you'd like to see the relationships of.

See http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html for inspiration and ideas.

```{r, solution = TRUE}
airbnb_df %>% filter(!is.na(neighbourhood_group)) %>% group_by(neighbourhood_group) %>% summarize(pricenew = mean(price, na.rm = T)) %>% ggplot(aes(x = neighbourhood_group, y = pricenew)) + geom_bar(stat="identity") + labs(title = "Relationship between Boroughs and Prices of AirBnbs") + xlab("Boroughs") + ylab("Prices") + scale_y_continuous(breaks = seq(0 , 1000, by = 25)) + theme_bw()
```

### Conclusion

Write up your thoughts about this data science project here and answer the following questions:

- What did we find out about our questions?
We found out that there are relationships between different variables in the Airbnb data, mainly between room types of Airbnbs and the price of those room types. For example, we had discovered through creating a bar graph that specific room types like hotels are more expensive than other room types.

- How did we explore our questions?
We extracted Airbnb data from a CSV file and put it into a dataframe. We then cleaned the data in the data frame and plotted data and created graphs based on the variables in the cleaned Airbnb data to visualize the relationship between vairables.

- What did our explorations show us?
For some variables, there seems to be a relationship between each other. For price and room types, not all room types are the same price, with some room types being more expensive than others. 

- What follow up data science questions arise for you regarding this candy dataset now that we've explored it some?
What other variables in the Airbnb data have a potential relationship with each other.

## Print out session info

Session info is a good thing to print out at the end of your notebooks so that you (and other folks) referencing your notebooks know what software versions and libraries you used to run the notebook.

```{r}
sessionInfo()
```
